%-------------------------
% Resume in Latex
% Author : Gieonne Sabijon
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Gieonne Sabijon} \\ \vspace{1pt}
    \small (905)-995-2711 $|$ \href{mailto:gieonnesabijon@gmail.com}{\underline{gieonnesabijon@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/gieonne/}{\underline{linkedin.com/in/gieonne}} $|$
    \href{https://github.com/gieonneSabijon}{\underline{github.com/gieonneSabijon}}$|$
    \href{https://www.gieonnesabijon.com}{\underline{gieonnesabijon.com}}
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ontario Tech University}{Oshawa, Ontario}
      {Bachelor of Science (Honours) Computer Science}{Sep. 2021 -- May 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Warehouse Order Picker}{June 2021 -- August 2021}
      {Burgham Sales}{Pickering, ON}
      \resumeItemListStart
        \resumeItem{Worked with inventory tracking software and handheld scanning devices to manage warehouse data accurately.}
        \resumeItem{Investigated and resolved inventory discrepancies to ensure accurate stock records}
        \resumeItem{Coordinated with team members to prioritize urgent orders and maintain workflow efficiency}
        \resumeItem{Adapted quickly to new software tools and warehouse technologies}
      \resumeItemListEnd

    \resumeSubheading
      {OTU Computer Science Club Member}{Sept 2023 -- May 2025}
      {Ontario Tech University}{Oshawa, ON}
      \resumeItemListStart
        \resumeItem{Engaged with a community of students passionate about computer science, technology, and software development.}
        \resumeItem{Attended technical presentations and professional development sessions to expand knowledge of computer science concepts.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ClipSphere} $|$ \emph{Flutter, Dart, Firebase Authentication, Cloud Firestore, Firebase Storage}}{March 2025 -- April 2025}
          \resumeItemListStart
            \resumeItem{Developed a cross-platform mobile application using Flutter that enables users to create accounts, upload videos, and interact with content in a social media environment.}
            \resumeItem{Built a scalable backend using Cloud Firestore to store user profiles, video metadata, comments, and user data}
            \resumeItem{Integrated cloud-based authentication, database, and storage services to create a scalable full-stack mobile application.}
            \resumeItem{Designed and developed responsive user interfaces with reusable Flutter widgets to improve maintainability and user experience.}
            \resumeItem{Implemented real-time database synchronization using Firestore streams to enable live updates across users and devices.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{TutorSeed} $|$ \emph{React, Next.js, Artifical Intelligence}}{July 2025 --  August 2025}
          \resumeItemListStart
            \resumeItem{Built an AI-powered learning platform that uses Socratic questioning to guide users through problem-solving instead of providing direct answers.}
            \resumeItem{Designed prompt engineering workflows to enforce step-by-step reasoning, adaptive guidance, and a growth-focused learning style.}
            \resumeItem{Developed a responsive web application using Next.js and React for an interactive tutoring experience.}
            \resumeItem{Integrated large language model APIs to provide dynamic, context-aware tutoring across programming and academic subjects.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{Ontario Tech ICS Generator} $|$ \emph{Webscraping, icalendar, REST API, Python}}{September 2024 --  September 2024}
          \resumeItemListStart
            \resumeItem{Built a CLI tool that generates .ics calendar files from Ontario Tech course schedules for easy import into Google Calendar and other calendar apps.}
            \resumeItem{Implemented web scraping and API-based authentication to securely retrieve student schedule data from university systems.}
            \resumeItem{Automated the conversion process to eliminate manual scheduling and improve usability for students.}
            \resumeItem{Created a lightweight Flask backend with a simple frontend for easy event setup and management.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++/C\#, SQL, JavaScript, HTML/CSS, R, Dart, Typescript, LaTeX} \\
     \textbf{Frameworks}{: React, Node.js, Next.js, Flask, Firebase, WordPress, Google Cloud Platform, PyTorch, TensorFlow, Express.js} \\
     \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, PyCharm, IntelliJ, Eclipse, Unity, Overleaf} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Dart SDK, React Hooks, Firebase SDK, BeautifulSoup, iCalendar, OpenAI API, Gemini API, PyGame, Flask} 
    }} \\
 \end{itemize}


%-------------------------------------------
\end{document}
